Data-efficient Motor-skills Learning in Latent Spaces for Robotic Clothing Assistance

### 2016-11-05 Paper/paper.tex
[major] first draft of paper based on rsj paper

\documentclass[a4paper]{article}

\usepackage{url}
\usepackage{cite}
\usepackage{array}
\usepackage{comment}
\usepackage{multirow}
\usepackage{booktabs}
\usepackage{amsfonts}
\usepackage{rsj2016e_IS}
\usepackage[cmex10]{amsmath}
\usepackage[pdftex]{graphicx}
\usepackage[caption=false,font=footnotesize]{subfig}

@@

\begin{document}
\title{Motor-skill Learning in Latent Spaces for Robotic Clothing Assistance}
\author{Nishanth Koganti$^{a,b}$, Ravi P. Joshi$^b$, Tomoya Tamei$^a$, Kazushi Ikeda$^a$, Tomohiro Shibata$^b$\\($^a$Graduate School of Information Science, Nara Institute of Science and Technology)\\($^b$Graduate School of Life Science and Systems Engineering, Kyushu Institute of Technology)}
\engtitle{}
\engauthor{}

\maketitle
\pagestyle{empty}
\thispagestyle{empty}
\setlength{\baselineskip}{4.4mm}

@@

\small{
\begin{thebibliography}{15}
\bibitem{yamazaki}
K. Yamazaki, R. Oya, K. Nagahama, K. Okada, and M. Inaba, ``Bottom dressing by a life-sized humanoid robot provided failure detection and recovery functions'' in Proc. of the IEEE Intl. Conf. on System Integration (SII), 2014.

@@

\end{thebibliography}
}
\normalsize

>>>>

\documentclass{article}

\usepackage[final,nonatbib]{nips_2016}

\usepackage{url}
\usepackage{amsmath}
\usepackage{booktabs}
\usepackage{hyperref}
\usepackage{amsfonts}
\usepackage{nicefrac}
\usepackage{microtype}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[pdftex]{graphicx}
\usepackage[caption=false,font=footnotesize]{subfig}

@@

\title{Data-efficient Motor-skills Learning in Latent Spaces for Robotic Clothing Assistance}

\author{
  Nishanth Koganti$^{1,2}$, Tomoya Tamei$^{1}$, Kazushi Ikeda$^{1}$, Tomohiro Shibata$^{2}$\\
  $^1$ Nara Institute of Science and Technology, Japan~~~$^2$ Kyushu Institute of Technology, Japan\\
  \texttt{\{nishanth-k,tomo-tam,kazushi\}@is.naist.jp, tom@brain.kyutech.ac.jp} \\
}

\begin{document}

\maketitle

\begin{abstract}
Robotic implementation of clothing assistance can greatly improve the quality-of-life for the elderly and disabled. This is still considered an open problem as it involves close interaction of the robot with non-rigid clothing articles and the assisted person with varying posture. In this study, we propose a data-efficient representation to encode task specific motor-skills of the robot using Bayesian nonparametric latent manifold learning. We implement our framework in a practical setting with a dual-arm robot performing clothing tasks. We demonstrate that performing motor-skills learning in such task specific latent spaces outperforms learning in the high-dimensional joint configuration space of the robot. Furthermore, our framework can also be used as a tool for learning from demonstration to impart novel skills to the robot.
\end{abstract}

@@

\small

\begin{thebibliography}{15}
\bibitem{yamazaki}
K. Yamazaki, R. Oya, K. Nagahama, K. Okada, and M. Inaba, ``Bottom dressing by a life-sized humanoid robot provided failure detection and recovery functions'' in Proc. of the IEEE Intl. Conf. on System Integration (SII), 2014.

@@

\end{thebibliography}
